---
title: "Week 4 Assignment"
output:
  html_document:
    df_print: paged
---



```{r}

library(caret)
library(kernlab)
library(dplyr)
library(rpart)
library(rpart.plot)
library(ggplot2)
library(lattice)
library(knitr)
library(rmarkdown)
```
#### Reading training and testing data

```{r}
training<-read.csv('pml-training.csv')
testing<-read.csv("pml-testing.csv")

```

#### Checking Dimensions of data
```{r}
dim(training)
dim(testing)
```
#### Classes that exist in Classe Column
```{r}
distinct(select(training,classe))
```
#### Removing near zero Var. cols
```{r}
non_zero_var<-nearZeroVar(training)
new_training<-training[,-non_zero_var]
new_testing<-testing[,-non_zero_var]
dim(new_training)
dim(new_testing)
```
#### removing cols that have more than 95% of nan values
```{r}
nan_cols<-sapply(new_training, function(c) mean(is.na(c)))>.95
new_training2<-new_training[,nan_cols==FALSE]
new_testing2<-new_testing[,nan_cols==FALSE]
dim(new_training2)
dim(new_testing2)
any(is.na(new_training2))
```

#### Choose cols from column 8 to the classe column
```{r}
f_training<-new_training2[,8:59]
f_testing<-new_testing2[,8:59]
```
#### separate data into training and testing
```{r}
inTrain<-createDataPartition(f_training$classe,p=.65,list = FALSE)
train_data<-f_training[inTrain,]
test_data<-f_testing[-inTrain,]
```
#### Build Rpart Model and prediction
```{r}
dt_model<-train(classe~.,data = train_data,method='rpart')
dt_pred<-predict(dt_model,test_data)
confusionMatrix(dt_model, test_data$classe)
rpart.plot(dt_model$finalModel, roundint=FALSE)

```

#### Build RF model and prediction
```{r}
f_model<-train(classe~.,data=train_data,method='rf')
rf_pred<-predict(rf_model,test_data)
RF_pred_Matrix<-confusionMatrix(rf_pred, test_data$classe)
print(RF_pred_Matrix)
```
#### Build RF model and prediction
```{r}
rf_model<-train(classe~.,data=train_data,method='rf')
rf_pred<-predict(rf_model,test_data)
RF_pred_Matrix<-confusionMatrix(rf_pred, test_data$classe)
print(RF_pred_Matrix)
```
#### build GBM 
```{r}
GBM_model <- train(classe ~ ., data = train_data, method = "gbm", verbose = FALSE)
print(GBM_model$finalModel)
GBM_pred <- predict(GBM_model, test_data)
GBM_pred_Matrix <- confusionMatrix(GBM_pred, test_data$classe)
print(GBM_pred_Matrix)
```

